---
title: "Learning Markdown"
author: "Jose Barrero"
date: "08/04/2020"
output: html_document
---

# Title
create some **bold** text or _italics_

```
a block of code
```

* bold with double asterisks
* italics with underscores
* code with 3 backticks


1. bold with double asterisks
2. italics with underscores
3. code with 3 backticks

## 2nd level header

First code chunk

```{r, echo=FALSE, message = TRUE, results = 'hide'}
library(tidyverse)
gapminder <- read_csv("data/gapminder.csv")

```

Second code chunk

```{r, echo=TRUE, message = TRUE, results = 'hide'}
gapminder %>%
  filter(country == "Australia") %>%
  ggplot(aes(x = pop, y = year)) +
  geom_point()
```


Third code chunk

```{r, echo=FALSE, message = TRUE, results = 'show'}
aus_data <- filter(gapminder, country == "Australia")
aus_data
```


### 3rd level header

[Link to these notes](https://csiro-data-school.github.io/rmarkdown/)

You can do subscripts with F~subscripts~ and superscripts with F^superscripts^

Sentence that requires a footnote [^1].

[^1]: Footnote text





